Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-22 WRITEUP/table_obsprop.tex
revised with DR's comments

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Observed Properties of RXJ1131 and its companion}
\tablehead{
\colhead{Parameter} &
\colhead{Unit} &
\colhead{Value}
}
\startdata
$z_{\rm CO}$   &                          & 0.6541\pmm0.0002 \\ [0.5ex]
$I_{\rm CO(2-1)}$     & Jy\,km s\pmOne           & 20.3\pmm0.6 \\ [0.5ex]
S$_{\bco}$     & Jy km s\pmOne beam\pmOne & 8.12\pmm0.30 \\ [0.5ex]
FWHM$_{\rm CO(2-1)}$ \tna & km s\pmOne               & 179\pmm9, 255\pmm28 \\ [0.5ex]
FWHM$_{\rm CO(2-1)}$\tnb        & km s\pmOne               & 220\pmm72 \\ [0.5ex]
$I_{\rm CO(3-2)}$     & Jy\,km s\pmOne           & 35.7\pmm6.9
\enddata
\label{tab:obsprop}
%\tablecomments{}
\tablenotetext{a}{From fitting a double Gaussian to the observed \bco spectrum (\Fig{CO21spec}).}
\tablenotetext{b}{From fitting a double Gaussian with a common FWHM to the de-lensed \bco spectrum (\Fig{delensed}).}
\end{deluxetable}

>>>>

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Observed Properties of RXJ1131 and its companion}
\tablehead{
\colhead{Parameter} &
\colhead{Unit} &
\colhead{Value}
}
\startdata
$z_{\rm CO(2-1)}$   &                          & 0.6541\pmm0.0002 \\ [0.5ex]
$I_{\rm CO(2-1)}$     & Jy\,km s\pmOne           & 20.3\pmm0.6 \\ [0.5ex]
$S_{\rm CO(2-1)}$\tna     & Jy km s\pmOne beam\pmOne & 8.12\pmm0.30 \\ [0.5ex]
FWHM$_{\rm CO(2-1)}$ \tnb & km s\pmOne               & 179\pmm9, 255\pmm28 \\ [0.5ex]
FWHM$_{\rm CO(2-1)}$\tnc        & km s\pmOne               & 220\pmm72 \\ [0.5ex]
$I_{\rm CO(3-2)}$     & Jy\,km s\pmOne           & 35.7\pmm6.9
\enddata
\label{tab:obsprop}
%\tablecomments{}
\tablenotetext{a}{Peak flux density in the intensity map.}
\tablenotetext{b}{From fitting a double Gaussian to the observed \bco spectrum (\Fig{CO21spec}).}
\tablenotetext{c}{From fitting a double Gaussian with a common FWHM to the de-lensed \bco spectrum (\Fig{delensed}).}
\end{deluxetable}
